Zero-inflated models

### 2024-06-22 src/count_completed.Rmd
Update 2021 files

```{r md_links}
c_text <- "page_update: "
f_text <- "\[sim1\]\: "
md_files$page_update_line <- "999"
md_files$old_link <- "999"
for (i_row in 1:nrow(md_files)) {
  full_file_name <- glue("{md_path}/{md_files$yr[i_row]}/{md_files$fn[i_row]}")
  read_lines(full_file_name) -> file_text
  file_text %>%
    str_subset(fixed(c_text)) %>%
    str_replace(fixed(c_text), "") -> page_update
  file_text %>%
    str_subset(f_text) %>%
    str_replace(f_text, "") %>%
    paste0("", collapse=", ") -> old_link
  n <- length(page_update)
  if (n > 1) {
    cat(
      glue(
        "\n\n{n} duplicates found in {full_file_name}.\n\n"))}
  page_update %>%
    paste0("", collapse=", ") -> md_files$page_update_line[i_row]
  md_files$old_link[i_row] <- old_link
}
count(md_files, page_update_line)
# count(md_files, yr, page_update_line)
```

@@

### Pages with page_update = `r (update_text="n")`

>>>>

```{r md_links}
c_text <- "page_update: "
f_text <- "\\[sim1\\]\\: "
md_files$page_update_line <- "999"
md_files$old_link <- "999"
for (i_row in 1:nrow(md_files)) {
  full_file_name <- glue("{md_path}/{md_files$yr[i_row]}/{md_files$fn[i_row]}")
  read_lines(full_file_name) -> file_text
  file_text %>%
    str_subset(fixed(c_text)) %>%
    str_replace(fixed(c_text), "") -> page_update
  file_text %>%
    str_subset(f_text) %>%
    str_replace(f_text, "") %>%
    paste0("", collapse=", ") -> old_link
  n <- length(page_update)
  if (n > 1) {
    cat(
      glue(
        "\n\n{n} duplicates found in {full_file_name}.\n\n"))}
  page_update %>%
    paste0("", collapse=", ") -> md_files$page_update_line[i_row]
  md_files$old_link[i_row] <- old_link
}
count(md_files, page_update_line)
# count(md_files, yr, page_update_line)
```

@@

### Pages with page_update = `r (update_text="no")`

### 2024-06-22 text/21/blogdown-first-steps.Rmd
Update 2021 files

---
title: "First steps with blogdown"
author: "Steve Simon"
source: new
date: "2021-10-09"
categories:
- Blog post
tags:
- Website details
output: html_document
---

>>>>

---
title: "First steps with blogdown"
author: "Steve Simon"
source: new
date: "2021-10-09"
categories:
- Blog post
tags:
- Website details
output: html_document
page_update: complete
---

### 2024-06-22 text/21/cubic-splines.Rmd
Update 2021 files

---
title: "Basics of cubic spline models"
author: "Steve Simon"
date: "2021-11-01"
categories:
- Recommendation
tags:
- Linear regression
output: html_document
---

>>>>

---
title: "Basics of cubic spline models"
source: new
author: "Steve Simon"
date: "2021-11-01"
categories:
- Recommendation
tags:
- Linear regression
output: html_document
page_update: complete
---

### 2024-06-22 text/21/dark-side.Rmd
Update 2021 files

---
title: "The dark side of big data"
source: new
date: "2021-10-28"
categories:
- Blog post
tags:
- Data science
- Incomplete page
output: html_document
---

>>>>

---
title: "The dark side of big data"
source: new
date: "2021-10-28"
categories:
- Blog post
tags:
- Data science
- Incomplete page
output: html_document
page_update: complete
---

### 2024-06-22 text/21/direct-standardization.Rmd
Update 2021 files

---
title: "Direct standardization of mortality rates"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Epidemiology
output: html_document
---

>>>>

---
title: "Direct standardization of mortality rates"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Epidemiology
output: html_document
page_update: complete
---

### 2024-06-22 text/21/glm-deviance.Rmd
Update 2021 files

---
title: "Deviance in a generalized linear model"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Deviance in a generalized linear model"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
page_update: complete
---

### 2024-06-22 text/21/hurricane-frequencies.Rmd
Update 2021 files

---
title: "Overfitting example using hurricane frequencies"
author: "Steve Simon"
source: new
date: "2021-12-11"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Overfitting example using hurricane frequencies"
author: "Steve Simon"
source: new
date: "2021-12-11"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
page_update: complete
---

### 2024-06-22 text/21/negative-binomial-regression.Rmd
Update 2021 files

---
title: "Working with negative binomial regression"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
- Generalized linear model
output: html_document
---

>>>>

---
title: "Working with negative binomial regression"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
- Generalized linear model
output: html_document
page_update: complete
---

### 2024-06-22 text/21/poisson-inferences.Rmd
Update 2021 files

---
title: "Working with the Poisson distribution"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---

>>>>

---
title: "Working with the Poisson distribution"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
page_update: complete
---

### 2024-06-22 text/21/poisson-regression.Rmd
Update 2021 files

---
title: "Working with Poisson regression"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---

@@

```{}
   2141
 x 2123
 ------
   6423
  4282
 2141
4282
-------
4545343
```

>>>>

---
title: "Working with Poisson regression"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
page_update: complete
---

@@

```{}
   2141
 x 2123
 ------
   6423
  4282
 2141
4282
page_update: complete
-------
4545343
```

### 2024-06-22 text/21/quasi-likelihood.Rmd
Update 2021 files

---
title: "Quasi-likelihood models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Quasi-likelihood models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
page_update: complete
---

### 2024-06-22 text/21/read-acs-data.Rmd
Update 2021 files

---
title: "Reading information from the American Community Survey into R"
source: new
date: "2021-09-29"
categories:
- Recommendation
tags:
- Website details
output: html_document
---

>>>>

---
title: "Reading information from the American Community Survey into R"
source: new
date: "2021-09-29"
categories:
- Recommendation
tags:
- Website details
output: html_document
page_update: complete
---

### 2024-06-22 text/21/venn-diagram.Rmd
Update 2021 files

---
title: "Test diagrams"
author: "Steve Simon"
source: new
date: "2021-10-30"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

>>>>

---
title: "Test diagrams"
author: "Steve Simon"
source: new
date: "2021-10-30"
categories:
- Blog post
tags:
- Graphical display
output: html_document
page_update: complete
---

### 2024-06-22 text/21/very-simple-splines.Rmd
Update 2021 files

---
title: "Very simple spline models"
author: "Steve Simon"
date: "2021-10-29"
categories:
- Recommendation
tags:
- Linear regression
output: html_document
---

>>>>

---
title: "Very simple spline models"
source: new
author: "Steve Simon"
date: "2021-10-29"
categories:
- Recommendation
tags:
- Linear regression
output: html_document
page_update: complete
---

### 2024-06-22 text/21/zero-inflated-poisson.Rmd
Update 2021 files

---
title: "Zero-inflated models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Zero-inflated models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
page_update: complete
---
